The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-06-15 manuscript/5pillars.Rmd
fixed dvcs figure

labs <- c("Developer 1",
  "Local Repository",
  "Working Files",
  "Developer 2",
  "Local Repository",
  "Working Files",
  "Developer 3",
  "Local Repository",
  "Working Files")

>>>>

labs <- c("Developer 1",
  "Working Files",
  "Local Repository",
  "Developer 2",
  "Working Files",
  "Local Repository",
  "Developer 3",
  "Working Files",
  "Local Repository")
